---
output:
  github_document:
    toc: true
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dpi = 300,
  out.width = "100%"
)
knitr::read_chunk("inst/r_code/study.R")

```

# RPack.PIRA

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

This is the analysis behind the
_Assessment of Disability Progression Independent of Relapse and Brain MRI
Activity in Patients with Multiple Sclerosis in Poland_
[@Kapica-Topczewska2021],
a peer-reviewed paper available at: <https://www.mdpi.com/2077-0383/10/4/868>.
The code has not been further optimised but reproduces with fidelity
the reported results.


## Installation

You can install the released version of `RPack.PIRA` from
[GitHub](https://github.com/FCACollin/rpack_pira) with:

``` r
# install.packages("devtools")
devtools::install_github("FCACollin/rpack_pira")
```

## Analysis Run

```{r setup}
```

### Patient characteristics

```{r table_01, results = "asis"}
```

### Disease progression and relapses

```{r fig_01, fig.width = 7.5, fig.height = 8, fig.cap = captions("fig1")}
```

```{r fig_02, fig.width = 7, fig.height = 4, fig.cap = captions("fig2")}
```

### Disease progression and MRI Activity

```{r fig_03, fig.width = 7, fig.height = 4, fig.cap = captions("fig3")}
```

```{r fig_04, fig.width = 7, fig.height = 4, fig.cap = captions("fig4")}
```

```{r fig_05, fig.width = 7.5, fig.height = 8, fig.cap = captions("fig5")}
```

### Disease progression: relapses and MRI Activity

```{r fig_06, fig.width = 7.5, fig.height = 8, fig.cap = captions("fig6")}
```

### Modele: Probability of Disease Worsening

```{r mod_glm_fit}
```

```{r mod_glm_devianceTable}
```

```{r mod_glm_effecttests}
```

```{r mod_glm_adj_means}
```

### Data

```{r}
knitr::kable(head(ADPIRA))
```

## References

[modeline]: # ( vim: set foldlevel=0 spell spelllang=en_gb: )
